### 2022-01-14 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_transfer@667f48eb27acd2dd82781f05f5b932dfddb8526e 🚀
Deploying to gh-pages from @ PoisotLab/ms_metaweb_transfer@ac7854fa5de6288a3f05d20a567f0a4b5f77d7e3 🚀

\hypertarget{results-and-discussion-of-the-case-study}{%
\section{Results and discussion of the case
study}\label{results-and-discussion-of-the-case-study}}

@@

Using a transfer learning framework we were able to construct a
probabilistic metaweb and (as as per Dunne, 2006) it is a list of
potential interactions and does not mean that they will exist wherever
the two species co-occur. The t-SVD embedding is able to learn relevant
ecological features for the network. fig.~\ref{fig:degree} shows that
the first rank correlates linearly with generality and vulnerability
(Schoener, 1989), \emph{i.e.} the number of preys and predators for each
species. Importantly, this implies that a rank 1 approximation
represents the configuration model for the metaweb, \emph{i.e.} a set of
random networks generated from a given degree sequence (Park \& Newman,
2004). Accounting for the probabilistic nature of the degrees, the rank
1 approximation also represents the \emph{soft} configuration model (van
der Hoorn et al., 2018). Both models are maximum entropy graph models
(Garlaschelli et al., 2018), with sharp (all network realizations
satisfy the specified degree sequence) and soft (network realizations
satisfy the degree sequence on average) local constraints, respectively.
The (soft) configuration model is an unbiased random graph model widely
used by ecologists in the context of null hypothesis significance
testing of network structure (\emph{e.g.} Bascompte et al., 2003) and
can provide informative priors for Bayesian inference of network
structure (\emph{e.g.} J.-G. Young et al., 2021). It is noteworthy that
for this metaweb, the relevant information was extracted at the first
rank. Because the first rank corresponds to the leading singular value
of the system, the results of fig.~\ref{fig:degree} have a
straightforward interpretation: degree-based processes are the most
important in structuring the mammalian food web.

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

>>>>

\hypertarget{results-and-discussion}{%
\section{Results and discussion}\label{results-and-discussion}}

@@

Using a transfer learning framework we were able to construct a
probabilistic metaweb and (as per Dunne, 2006) is a list of potential
interactions, meaning that they will not necessarily exist wherever the
two species co-occur. The t-SVD embedding is able to learn relevant
ecological features for the network. fig.~\ref{fig:degree} shows that
the first rank correlates linearly with generality and vulnerability
(Schoener, 1989), \emph{i.e.} the number of preys and predators for each
species. Importantly, this implies that a rank 1 approximation
represents the configuration model for the metaweb, \emph{i.e.} a set of
random networks generated from a given degree sequence (Park \& Newman,
2004). Accounting for the probabilistic nature of the degrees, the rank
1 approximation also represents the \emph{soft} configuration model (van
der Hoorn et al., 2018). Both models are maximum entropy graph models
(Garlaschelli et al., 2018), with sharp (all network realizations
satisfy the specified degree sequence) and soft (network realizations
satisfy the degree sequence on average) local constraints, respectively.
The (soft) configuration model is an unbiased random graph model widely
used by ecologists in the context of null hypothesis significance
testing of network structure (\emph{e.g.} Bascompte et al., 2003) and
can provide informative priors for Bayesian inference of network
structure (\emph{e.g.} J.-G. Young et al., 2021). It is noteworthy that
for this metaweb, the relevant information was extracted at the first
rank. Because the first rank corresponds to the leading singular value
of the system, the results of fig.~\ref{fig:degree} have a
straightforward interpretation: degree-based processes are the most
important in structuring the mammalian food web.
